---
title: "Asynchronous Usage with coinbase"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Asynchronous Usage with coinbase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

box::use(
  coinbase[CoinbaseMarketData, CoinbaseTrading, CoinbaseAccount, get_api_keys],
  coro[async, await],
  later[run_now, loop_empty],
  promises[then, catch, promise_all]
)

box::use(
  connectcore[local_mock_api],
  ../tests/testthat/mock_router[.mock_routes]
)

local_mock_api(.mock_routes)

# Throwaway, ephemeral EC P-256 key for the authenticated examples. It signs the
# JWT before the request is sent (so the key must be loadable), but the mock
# router ignores the Authorization header entirely: it grants nothing, touches
# no funds, and is regenerated on every build.
.sk <- openssl::ec_keygen("P-256")
KEYS <- list(
  api_key_name = "organizations/00000000-0000-0000-0000-000000000000/apiKeys/00000000-0000-0000-0000-000000000000",
  api_private_key = openssl::write_pem(.sk)
)
```

Every R6 class in `coinbase` accepts an `async = TRUE` flag at construction.
When enabled, all methods return `promises::promise` objects instead of
direct values. This vignette shows how to consume those promises with
`coro::async`/`await` and `later::run_now`.

The examples below execute against a built-in mock of the Coinbase API, so the
printed output is real, deterministic data produced with no network, no
credentials, and no funds.

## Disclaimer

This software is provided for educational and research purposes. Trading
cryptocurrency carries substantial risk. You are solely responsible for any
orders placed through this package. Use the order **preview** methods (which
execute nothing) before placing live orders. The trading examples below run
against the public market-data host where they need no auth; the order
examples require credentials and are illustrative only.

## Why Async?

Synchronous HTTP blocks the R session while waiting for a reply.
Asynchronous mode lets you fire off multiple requests and process results
as they arrive — useful for bots that poll several products or place orders
in parallel. The same `async` branch point covers every class:
`CoinbaseMarketData`, `CoinbaseAccount`, `CoinbaseTrading`, and
`CoinbaseFutures`.

## Setup

```{r load}
box::use(
  coinbase[CoinbaseMarketData, CoinbaseTrading, CoinbaseAccount, get_api_keys],
  coro[async, await],
  later[run_now, loop_empty],
  promises[then, catch, promise_all]
)
```

Public market data needs no credentials. For the authenticated classes,
store your CDP API key in `.Renviron` (the PEM newlines escaped as `\n` on a
single line) and let `get_api_keys()` read them — never hardcode secrets:

```bash
COINBASE_API_KEY_NAME="organizations/<org-uuid>/apiKeys/<key-uuid>"
COINBASE_API_PRIVATE_KEY="-----BEGIN EC PRIVATE KEY-----\n...\n-----END EC PRIVATE KEY-----\n"
```

```{r keys, eval = FALSE}
keys <- get_api_keys()
```

> **Event loop**: R does not have a built-in event loop like Node.js or
> Python's `asyncio`. Promises only resolve when the event loop ticks via
> `later::run_now()`. In scripts and vignettes, drain the loop with
> `while (!loop_empty()) run_now()`. In **Shiny** apps the event loop runs
> automatically.

---

## Basic Async: `coro::async` + `await`

The most ergonomic way to work with promises in R is `coro::async`, which
lets you write code that *looks* synchronous but runs asynchronously under
the hood — just like TypeScript's `async`/`await`. Pass `async = TRUE` to
any class constructor; its methods then return promises instead of
data.tables:

```{r async-basic}
market <- CoinbaseMarketData$new(async = TRUE)
ticker <- NULL

get_ticker <- async(function() {
  res <- await(market$get_ticker("BTC-USD"))
  ticker <<- res
  return(invisible(NULL))
})

get_ticker()
while (!loop_empty()) {
  run_now()
}
ticker
```

> **Key pattern**: define an `async` function, `await` each API call,
> capture the result with `<<-`, drive the event loop with
> `while (!loop_empty()) run_now()`.

The resolved value is a single-row `data.table` with numeric `ask`, `bid`,
`price`, `size`, `volume`, and a POSIXct `time`.

---

## Sequential Async: Multiple `await` Calls

Chain several awaited calls in sequence — each one resolves before the next
begins, just like `await` in TypeScript:

```{r async-sequential}
market <- CoinbaseMarketData$new(async = TRUE)
results <- NULL

fetch_data <- async(function() {
  ticker <- await(market$get_ticker("BTC-USD"))
  ohlcv <- await(market$get_ohlcv("BTC-USD", granularity = "1min"))
  results <<- list(ticker = ticker, ohlcv = ohlcv)
  return(invisible(NULL))
})

fetch_data()
while (!loop_empty()) {
  run_now()
}
results$ticker
results$ohlcv
```

The `ohlcv` element is a `data.table` with columns `datetime`, `open`,
`high`, `low`, `close`, `volume`.

---

## Concurrent Requests with `promise_all`

When requests are independent, fire them simultaneously and collect all
results at once — the async equivalent of `Promise.all()` in TypeScript:

```{r async-parallel}
market <- CoinbaseMarketData$new(async = TRUE)
results <- NULL

fetch_parallel <- async(function() {
  # Launch both requests concurrently — no await yet, just collect promises
  ticker_promise <- market$get_ticker("BTC-USD")
  candles_promise <- market$get_ohlcv("BTC-USD", granularity = "1hour")
  # Await them together — like Promise.all([ticker, candles])
  res <- await(promise_all(ticker = ticker_promise, candles = candles_promise))
  results <<- res
  return(invisible(NULL))
})

fetch_parallel()
while (!loop_empty()) {
  run_now()
}
results$ticker
results$candles
```

---

## Practical Example: Polling Several Endpoints Concurrently

A common use case is gathering several views of a product at once — the
ticker, recent candles, recent trades, and the order book. With async mode,
all requests fly in parallel rather than sequentially:

```{r multi-symbol}
market <- CoinbaseMarketData$new(async = TRUE)
snapshot <- NULL

fetch_snapshot <- async(function() {
  # Fire all requests concurrently
  promises <- list(
    ticker = market$get_ticker("BTC-USD"),
    candles = market$get_ohlcv("BTC-USD", granularity = "1min"),
    trades = market$get_trades("BTC-USD", limit = 100),
    orderbook = market$get_orderbook("BTC-USD", level = 2)
  )

  # Await all at once
  res <- await(do.call(promise_all, promises))
  snapshot <<- res
  return(invisible(NULL))
})

fetch_snapshot()
while (!loop_empty()) {
  run_now()
}

# Each element is the parsed data.table for one endpoint
snapshot$ticker
snapshot$orderbook
```

The same `lapply` + `do.call(promise_all, ...)` shape scales to a watchlist:
build one promise per product, name the list by product id, and await them
together.

---

## Promise Chaining with `then` / `catch`

If you prefer the promise-pipeline style (common in JavaScript), resolve a
promise with `then` and handle rejection with `catch`. This is the
alternative to `coro::async`/`await`:

```{r promise-chain}
market <- CoinbaseMarketData$new(async = TRUE)
chain_result <- NULL

stats_promise <- market$get_ohlcv("BTC-USD", granularity = "1hour")
handled <- then(stats_promise, function(ohlcv) {
  chain_result <<- ohlcv
  return(invisible(NULL))
})
catch(handled, function(err) {
  message("Error: ", conditionMessage(err))
  return(invisible(NULL))
})

while (!loop_empty()) {
  run_now()
}
chain_result
```

---

## Async Trading Example

Trading methods return promises in async mode just like market data. Always
**preview** an order (a dry run that places nothing) before submitting a live
one. Sequential `await` keeps the flow readable.

Construct the client with your credentials (read from `.Renviron` via
`get_api_keys()`):

```{r async-trading-init}
trading <- CoinbaseTrading$new(async = TRUE)
```

```{r async-trading-init-hidden, echo = FALSE}
trading <- CoinbaseTrading$new(keys = KEYS, async = TRUE)
```

```{r async-trading}
results <- NULL

preview_then_query <- async(function() {
  # Dry run — executes nothing; validates the configuration
  preview <- await(trading$preview_order(
    "BTC-USD",
    "BUY",
    list(market_market_ioc = list(quote_size = "10"))
  ))

  # Query recent orders for this product
  orders <- await(trading$get_orders(product_ids = "BTC-USD", limit = 10))

  results <<- list(preview = preview, orders = orders)
  return(invisible(NULL))
})

preview_then_query()
while (!loop_empty()) {
  run_now()
}
results$preview[, .(order_total, commission_total, base_size, best_ask, errs)]
results$orders[, .(order_id, product_id, side, status, order_type, filled_size)]
```

To place a live order, call `add_order()` instead of `preview_order()`. It
takes the same `product_id`, `side`, and `order_configuration`, plus optional
`client_order_id`, `self_trade_prevention_id`, `leverage`, `margin_type`, and
`retail_portfolio_id`; it resolves to a single-row `data.table` with
`success`, the scalar `order_id`, `product_id`, `side`, `client_order_id`,
and `failure_reason`.

---

## Error Handling with `tryCatch`

Inside `async` functions, use `tryCatch` around `await` calls for structured
error handling — `await()` re-throws the promise rejection as a normal R
error, so the try/catch pattern works directly. Here a malformed product id
is rejected (validated before any request is sent) and caught:

```{r async-error-handling}
market <- CoinbaseMarketData$new(async = TRUE)
result <- NULL

safe_fetch <- async(function() {
  res <- tryCatch(
    await(market$get_ticker("NOTAVALIDSYMBOL")),
    error = function(e) {
      message("Caught error: ", conditionMessage(e))
      return(NULL)
    }
  )
  result <<- res
  return(invisible(NULL))
})

safe_fetch()
while (!loop_empty()) {
  run_now()
}
```

---

## Running the Event Loop

The critical piece of async R is the **event loop**. Promises do not resolve
until the event loop ticks. In an interactive session or Shiny app, the event
loop runs automatically. In scripts or vignettes, you must drive it manually.

```r
# Idiomatic event loop drain
while (!later::loop_empty()) {
  later::run_now()
}
```

Or with a timeout guard:

```r
deadline <- lubridate::now() + lubridate::seconds(30) # 30-second timeout
while (!later::loop_empty() && lubridate::now() < deadline) {
  later::run_now(timeoutSecs = 0.1)
}
```

In **Shiny** applications, the event loop is managed for you — simply return
promises from reactive expressions and Shiny handles resolution.

---

## `coro::await` Cheat Sheet

| Pattern | Works? | Notes |
|---------|--------|-------|
| `x <- await(promise)` | Yes | Standard pattern |
| `x <- await(obj$method(arg))` | Yes | Await wrapping a call is fine |
| `await(promise)` (bare, no assignment) | Yes | Side-effect only |
| `await` inside loops/if/tryCatch | Yes | Full control flow support |
| `x <<- await(promise)` | **No** | `<<-` not supported by coro |
| `f(await(promise))` | **No** | Nested inside function args |

> **Rule of thumb**: `await()` must appear as the RHS of a `<-` or as a bare
> statement — never inside another expression. Assign the result to a local
> with `<-`, then copy it out of the async body with `<<-` after the await
> returns.

---

## Choosing Sync vs Async

| Scenario | Recommendation |
|----------|---------------|
| Interactive exploration | **Sync** — simpler, results print immediately |
| Scripts fetching one endpoint | **Sync** — no event loop needed |
| Bots polling multiple products | **Async** — concurrent requests reduce latency |
| Shiny dashboards | **Async** — keeps the UI responsive |
| Deep tick backfills | Use `get_trades_history()` / `coinbase_backfill_trades()` (handle batching internally) |

---

## Next Steps

- See `vignette("getting-started")` for a tour of the package in synchronous mode.
- Review the `CoinbaseMarketData`, `CoinbaseAccount`, `CoinbaseTrading`, and
  `CoinbaseFutures` class documentation for full method coverage.
- Explore the [Coinbase Advanced Trade API
  documentation](https://docs.cdp.coinbase.com/advanced-trade/docs/welcome)
  for endpoint details.
