---
title: "Package Tour and Data-Shape Conventions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package Tour and Data-Shape Conventions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

# Package symbols used throughout this vignette.
box::use(
  coinbase[
    CoinbaseMarketData, CoinbaseAccount, CoinbaseTrading, CoinbaseFutures,
    get_api_keys, get_base_url, get_exchange_base_url,
    trades_to_ohlcv, verify_symbol, generate_client_order_id
  ]
)

# httr2 exposes a global mock hook: `options(httr2_mock = ...)` intercepts every
# req_perform / req_perform_promise call. Loading the shared router and setting
# the option makes every chunk below execute against canned, deterministic
# fixtures -- no network, no real credentials, no funds.
box::use(../tests/testthat/mock_router[mock_router])
options(httr2_mock = mock_router)

# coinbase signs a JWT with the private key BEFORE the request is performed, so
# the authenticated examples need a loadable key. We mint a THROWAWAY ephemeral
# EC P-256 key here: it signs the request fine, the mock ignores the
# Authorization header entirely, it grants nothing, and it is regenerated on
# every build. Never put a real key here.
.sk <- openssl::ec_keygen("P-256")
KEYS <- list(
  api_key_name = "organizations/00000000-0000-0000-0000-000000000000/apiKeys/00000000-0000-0000-0000-000000000000",
  api_private_key = openssl::write_pem(.sk)
)
```

This vignette is the **one-stop tour** of the `coinbase` package. It
catalogues every public method by class, gives the exact `data.table`
each one returns — column names and types — and then documents the
underlying data-shape policy in detail.

If you've never used the package, read top to bottom. If you've used
it and just want to know how a specific endpoint comes back, jump to
the catalogue table for its class and then to the column listings
below it.

The same conventions are shared with the sister `alpaca`, `binance`,
and `kucoin` packages, so that switching between exchanges does not
mean switching mental models of how the data looks. The defining
invariant on `coinbase` is the strongest of the four: **every method
returns a `data.table` with no list columns.** Coinbase's nested
`{value, currency}` monetary amounts are flattened to plain numerics,
fixed-schema nested objects (`fee_tier`, `order_configuration`,
`margin_window`) are collapsed into scalar columns, and error arrays
are joined to a single string — so a returned table never hides a
list cell.

Every example below is **live**: it runs against a built-in mock of
the Coinbase API, so the tables you see are exactly the shape the real
endpoints return.

---

## What's in the package

Four R6 classes plus a handful of standalone helpers wrap the Coinbase
Advanced Trade API (authenticated trading / account / futures) and the
public Coinbase Exchange API (market data). Every class supports both
**synchronous** and **asynchronous (promise-based)** operation via
`httr2`, selected by the `async` flag at construction. All four inherit
from a common abstract base (`CoinbaseBase`) that handles JWT signing,
sync/async dispatch, and body-cursor pagination.

| Class | What it covers |
|---|---|
| `CoinbaseMarketData` | Public market data on the Exchange host — products, candles (OHLCV), tick trades, deep trade history, order book, ticker, server time. No auth |
| `CoinbaseAccount` | Authenticated account data — trading accounts (balances), transaction/fee summary, portfolios, API-key permissions |
| `CoinbaseTrading` | Order management — place, preview, edit, edit-preview, cancel, and query orders + fills |
| `CoinbaseFutures` | US futures (Coinbase Financial Markets / CFM) — balance summary, positions, cash sweeps, intraday margin settings, margin window |

Standalone (not on a class):

| Helper | What it does |
|---|---|
| `get_api_keys()`, `get_base_url()`, `get_exchange_base_url()` | Read API credentials and base URLs from environment variables |
| `coinbase_build_request()` | Low-level HTTP / JWT-signing primitive — every method goes through this |
| `coinbase_backfill_trades()` | Bulk deep tick-history download for many products with CSV resume |
| `trades_to_ohlcv()` | Aggregate raw tick trades into OHLCV bars at any interval |
| `verify_symbol()` | Sanity-check a product ID's shape before placing an order |
| `generate_client_order_id()` | Fresh RFC-4122 v4 UUID for the `client_order_id` idempotency key |

---

## Setup

Coinbase Advanced Trade uses CDP key-pair credentials (a key `name`
plus a `privateKey`), not an API key / secret pair. Download the JSON
from <https://www.coinbase.com/settings/api> and store the two fields
in `.Renviron`. The multi-line `privateKey` is escaped onto one line
by replacing real newlines with the two characters `\n`;
`get_api_keys()` unescapes them back before signing.

```bash
COINBASE_API_KEY_NAME=organizations/<org-uuid>/apiKeys/<key-uuid>
COINBASE_API_PRIVATE_KEY=-----BEGIN EC PRIVATE KEY-----\n<...base64...>\n-----END EC PRIVATE KEY-----\n
```

The placeholders above are deliberately fake; never commit a real key.
Both EC keys (ES256) and base64 Ed25519 keys (EdDSA) are supported by
the signer.

Then in R, using `box::use` rather than `library()`. When the
environment variables are set, `get_api_keys()` reads them with no
arguments:

```{r setup-keys, eval = FALSE}
box::use(
  coinbase[
    CoinbaseMarketData, CoinbaseAccount, CoinbaseTrading,
    CoinbaseFutures, get_api_keys
  ]
)

keys    <- get_api_keys()                 # reads .Renviron
market  <- CoinbaseMarketData$new()       # public, no keys needed
account <- CoinbaseAccount$new(keys = keys)
trading <- CoinbaseTrading$new(keys = keys)
futures <- CoinbaseFutures$new(keys = keys)
```

---

## `CoinbaseMarketData` — public market data (Exchange host)

These endpoints hit the Exchange host
(`api.exchange.coinbase.com`), require no authentication, and expose
deep trade history. The `/candles` endpoint returns only ~300 bars per
call, so complete OHLCV at any timeframe is built from ticks: page
`get_trades_history()` (or run `coinbase_backfill_trades()`), then
aggregate with `trades_to_ohlcv()`.

| Method | Endpoint | Shape |
|---|---|---|
| `get_products()` | `GET /products` | one row per product |
| `get_product(product_id)` | `GET /products/{id}` | single row |
| `get_ohlcv(product_id, granularity, start, end)` | `GET /products/{id}/candles` | one row per candle |
| `get_trades(product_id, limit, after)` | `GET /products/{id}/trades` | one row per trade |
| `get_trades_history(product_id, start, end, max_pages)` | `GET /products/{id}/trades` (paged) | one row per trade, sorted ascending, de-duplicated |
| `get_orderbook(product_id, level)` | `GET /products/{id}/book` | long — one row per `(side, level)` |
| `get_ticker(product_id)` | `GET /products/{id}/ticker` | single row |
| `get_server_time()` | `GET /time` | single row |

Public market data needs no keys:

```{r market-init}
market <- CoinbaseMarketData$new()
```

### Products

`get_products()` and `get_product()` go through the generic
`as_dt_list` / `as_dt_row` flatteners: every scalar field becomes a
column, and any nested object or multi-element value the API returns
is collapsed to a single JSON string (never a list column). Field names
are snake_case. Numeric-looking fields are returned as the character
strings Coinbase sends — cast at the point of use.

```{r products}
products <- market$get_products()
products[]
```

A single product is the same row shape:

```{r product}
market$get_product("BTC-USD")[]
```

### OHLCV / candles

`get_ohlcv()` (parser `parse_candles`) reorders Coinbase's raw
`[time, low, high, open, close, volume]` array into the canonical
layout and sorts ascending. Exactly six columns:

| Column | Type | Notes |
|---|---|---|
| `datetime` | `POSIXct` (UTC) | bar start; from epoch seconds |
| `open` | `numeric` | |
| `high` | `numeric` | |
| `low` | `numeric` | |
| `close` | `numeric` | |
| `volume` | `numeric` | |

```{r ohlcv}
candles <- market$get_ohlcv("BTC-USD", granularity = "1min")
candles[, .(datetime, open, high, low, close, volume)]
```

`granularity` is one of `"1min"`, `"5min"`, `"15min"`, `"1hour"`,
`"6hour"`, `"1day"`.

### Trades

`get_trades()` and `get_trades_history()` (parser `parse_trades`)
return one row per tick trade, with exactly five typed columns:

| Column | Type | Notes |
|---|---|---|
| `trade_id` | `numeric` | |
| `side` | `character` | |
| `price` | `numeric` | |
| `size` | `numeric` | |
| `time` | `POSIXct` (UTC) | |

```{r trades}
trades <- market$get_trades("BTC-USD", limit = 1000L)
trades[]
```

To page deeper into history with `get_trades()`, pass the smallest
`trade_id` seen so far as `after`; `get_trades_history()` does this
loop for you and returns a single de-duplicated, ascending table:

```{r trades-history}
ticks <- market$get_trades_history("BTC-USD")
ticks[]
```

### Order book

`get_orderbook()` (parser `parse_orderbook`) is the one
**long-format** market-data method: the `bids` and `asks` arrays are
stacked into one table with a `side` column (`"bid"` / `"ask"`). The
shape of the third column depends on the requested `level`:

| Column | Type | Levels |
|---|---|---|
| `side` | `character` | all — `"bid"` / `"ask"` |
| `price` | `numeric` | all |
| `size` | `numeric` | all |
| `num_orders` | `numeric` | levels **1 and 2** (aggregated book) |
| `order_id` | `character` | level **3** only (non-aggregated book) |

At levels 1 and 2 the book is aggregated, so each entry's third
element is an order *count* (`num_orders`). At level 3 the book is the
full non-aggregated book, so the third element is an `order_id`
string; the parser emits it as a character `order_id` column instead
of coercing it to numeric. A given call returns one or the other,
never both.

```{r orderbook}
# Top 5 highest-priced asks (aggregated level-2 book)
depth <- market$get_orderbook("BTC-USD", level = 2L)
depth[side == "ask"][order(-price)][1:min(5, .N)]
```

At level 3 the third column is a character `order_id` instead of
`num_orders` (a single call returns one or the other, never both):

```{r orderbook-l3}
l3 <- market$get_orderbook("BTC-USD", level = 3L)
l3[, .(side, price, size, order_id)]
```

### Ticker and server time

`get_ticker()` returns a single row; the numeric fields (`ask`, `bid`,
`price`, `size`, `volume`, `rfq_volume` where present) are cast to
`numeric` and `time` to `POSIXct`, with any other fields (e.g.
`trade_id`) left as the API sends them.

```{r ticker}
market$get_ticker("BTC-USD")[]
```

`get_server_time()` returns a single row with `iso` and `epoch`:

```{r server-time}
market$get_server_time()[]
```

---

## `CoinbaseAccount` — accounts, fees, portfolios, permissions

All endpoints require credentials. `get_accounts()` walks Coinbase's
body-cursor pagination (`cursor` / `has_next`) to return every account
across pages.

| Method | Endpoint | Shape |
|---|---|---|
| `get_accounts(limit, max_pages)` | `GET /api/v3/brokerage/accounts` | one row per account |
| `get_account(account_uuid)` | `GET /api/v3/brokerage/accounts/{uuid}` | single row |
| `get_fees(product_type)` | `GET /api/v3/brokerage/transaction_summary` | single row |
| `get_portfolios()` | `GET /api/v3/brokerage/portfolios` | one row per portfolio |
| `get_key_permissions()` | `GET /api/v3/brokerage/key_permissions` | single row |

Construct the authenticated client with your keys:

```{r account-init}
account <- CoinbaseAccount$new()
```

```{r account-init-hidden, echo = FALSE}
account <- CoinbaseAccount$new(keys = KEYS)
```

### Accounts

`get_accounts()` / `get_account()` (parser `parse_accounts`) flatten
the nested `available_balance` / `hold` `{value, currency}` objects to
plain numerics. Exactly these columns:

| Column | Type |
|---|---|
| `uuid` | `character` |
| `name` | `character` |
| `currency` | `character` |
| `available_balance` | `numeric` (flattened from `{value, currency}`) |
| `hold` | `numeric` (flattened from `{value, currency}`) |
| `active` | `logical` |
| `default` | `logical` |
| `ready` | `logical` |
| `type` | `character` |
| `platform` | `character` |
| `retail_portfolio_id` | `character` |
| `created_at` | `POSIXct` (UTC) |
| `updated_at` | `POSIXct` (UTC) |

```{r accounts}
accts <- account$get_accounts()
accts[]
accts[available_balance > 0, .(currency, available_balance, hold)]
```

### Fees

`get_fees()` (parser `parse_fees`) flattens the nested `fee_tier`
object into scalar columns alongside the top-level volume/fee fields.
A single row, every column numeric except `pricing_tier`:

| Column | Type |
|---|---|
| `pricing_tier` | `character` |
| `maker_fee_rate` | `numeric` |
| `taker_fee_rate` | `numeric` |
| `usd_from` | `numeric` |
| `usd_to` | `numeric` |
| `total_volume` | `numeric` |
| `total_fees` | `numeric` |
| `total_balance` | `numeric` |

```{r fees}
account$get_fees()[]
```

Pass `product_type = "SPOT"` or `"FUTURE"` to scope the summary.

### Portfolios and key permissions

`get_portfolios()` returns one row per portfolio via the generic
`as_dt_list` flattener; `get_key_permissions()` returns a single row
via `as_dt_row`:

```{r portfolios}
account$get_portfolios()[]
account$get_key_permissions()[]
```

---

## `CoinbaseTrading` — order management

All endpoints require credentials. `get_orders()` and `get_fills()`
walk the body-cursor pagination. Orders carry an
`order_configuration` — a one-key list naming the detailed order type
(e.g. `market_market_ioc`, `limit_limit_gtc`,
`stop_limit_stop_limit_gtc`) — which the parsers flatten into scalar
columns (see Treatment C below).

| Method | Endpoint | Shape |
|---|---|---|
| `add_order(product_id, side, order_configuration, client_order_id, self_trade_prevention_id, leverage, margin_type, retail_portfolio_id)` | `POST /api/v3/brokerage/orders` | single row |
| `preview_order(product_id, side, order_configuration, leverage, margin_type, retail_portfolio_id)` | `POST /api/v3/brokerage/orders/preview` | single row |
| `get_order(order_id)` | `GET /api/v3/brokerage/orders/historical/{id}` | single row |
| `get_orders(product_ids, order_status, order_side, limit, order_ids, start_date, end_date, order_types, product_type, order_placement_source, contract_expiry_type, asset_filters, retail_portfolio_id, time_in_forces, sort_by, max_pages)` | `GET /api/v3/brokerage/orders/historical/batch` | one row per order |
| `get_fills(order_ids, trade_ids, product_ids, start_sequence_timestamp, end_sequence_timestamp, retail_portfolio_id, limit, sort_by, max_pages)` | `GET /api/v3/brokerage/orders/historical/fills` | one row per fill |
| `edit_order(order_id, price, size)` | `POST /api/v3/brokerage/orders/edit` | single row |
| `preview_edit_order(order_id, price, size)` | `POST /api/v3/brokerage/orders/edit_preview` | single row |
| `cancel_orders(order_ids)` | `POST /api/v3/brokerage/orders/batch_cancel` | one row per order |

Note the recently-widened signatures: `add_order()` / `preview_order()`
take `leverage`, `margin_type` (`"CROSS"` / `"ISOLATED"`), and
`retail_portfolio_id` (plus `self_trade_prevention_id` on `add_order`
only); `get_orders()` takes the full filter set above; and
`get_fills()` filters by `order_ids` (**plural**) and `trade_ids`, with
sequence-timestamp bounds and a `sort_by`.

```{r trading-init}
trading <- CoinbaseTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- CoinbaseTrading$new(keys = KEYS)
```

### Orders (`get_order` / `get_orders`)

Parser `parse_orders`, which flattens each order's `order_configuration`
via `flatten_order_config`. Exactly these columns, one row per order:

| Column | Type | Notes |
|---|---|---|
| `order_id` | `character` | |
| `client_order_id` | `character` | |
| `product_id` | `character` | |
| `side` | `character` | |
| `status` | `character` | |
| `order_type` | `character` | coarse API enum, e.g. `"LIMIT"` |
| `config_type` | `character` | detailed config key, e.g. `"limit_limit_gtc"` |
| `time_in_force` | `character` | |
| `created_time` | `POSIXct` (UTC) | |
| `completion_percentage` | `numeric` | |
| `filled_size` | `numeric` | |
| `average_filled_price` | `numeric` | |
| `number_of_fills` | `numeric` | |
| `filled_value` | `numeric` | |
| `total_fees` | `numeric` | |
| `base_size` | `numeric` | from `order_configuration` |
| `quote_size` | `numeric` | from `order_configuration` |
| `limit_price` | `numeric` | from `order_configuration` |
| `stop_price` | `numeric` | from `order_configuration` |
| `stop_trigger_price` | `numeric` | bracket trigger; from `order_configuration` |
| `stop_direction` | `character` | from `order_configuration` |
| `end_time` | `POSIXct` (UTC) | GTD expiry; from `order_configuration` |
| `post_only` | `logical` | from `order_configuration` |

```{r orders}
orders <- trading$get_orders(product_ids = "BTC-USD", limit = 50L)
orders[, .(order_id, product_id, side, status, order_type, config_type, filled_size)]
```

A single order by id is the same row shape:

```{r order}
trading$get_order("1111aaaa-2222-bbbb-3333-cccccccccccc")[
  , .(order_id, side, status, config_type, base_size, limit_price)
]
```

### Fills (`get_fills`)

Parser `parse_fills`, one row per fill, exactly:

| Column | Type |
|---|---|
| `entry_id` | `character` |
| `trade_id` | `character` |
| `order_id` | `character` |
| `product_id` | `character` |
| `side` | `character` |
| `trade_time` | `POSIXct` (UTC) |
| `trade_type` | `character` |
| `price` | `numeric` |
| `size` | `numeric` |
| `commission` | `numeric` |
| `size_in_quote` | `logical` |
| `liquidity_indicator` | `character` |

```{r fills}
fills <- trading$get_fills(product_ids = "BTC-USD", sort_by = "TRADE_TIME")
fills[]
```

### Preview (`preview_order`)

Parser `parse_preview`, a single row. `errs` collapses Coinbase's
error array (objects or bare strings) into one human-readable string —
`NA` when the preview validated cleanly.

| Column | Type |
|---|---|
| `order_total` | `numeric` |
| `commission_total` | `numeric` |
| `quote_size` | `numeric` |
| `base_size` | `numeric` |
| `best_bid` | `numeric` |
| `best_ask` | `numeric` |
| `slippage` | `numeric` |
| `errs` | `character` (collapsed; `NA` if none) |
| `preview_id` | `character` |

```{r preview-order}
# Validate without placing anything (dry run; executes nothing)
pv <- trading$preview_order(
  "BTC-USD", "BUY",
  list(market_market_ioc = list(quote_size = "10"))
)
pv[]
```

### Create-order (`add_order`)

Parser `parse_create_order`, a single row. The scalar `order_id` is
lifted out of the nested `success_response`, the failure/error objects
are collapsed to one `failure_reason` string, and the
`order_configuration` is flattened:

| Column | Type |
|---|---|
| `success` | `logical` |
| `order_id` | `character` |
| `product_id` | `character` |
| `side` | `character` |
| `client_order_id` | `character` |
| `failure_reason` | `character` (collapsed; `NA` on success) |
| `config_type` | `character` |
| `base_size` | `numeric` |
| `quote_size` | `numeric` |
| `limit_price` | `numeric` |
| `stop_price` | `numeric` |
| `stop_trigger_price` | `numeric` |

```{r add-order}
order <- trading$add_order(
  "BTC-USD", "BUY",
  list(market_market_ioc = list(quote_size = "10")),
  client_order_id = "client-001"
)
order[, .(success, order_id, product_id, side, client_order_id, failure_reason)]
```

### Edit, edit-preview, and cancel

| Method | Parser | Columns |
|---|---|---|
| `edit_order()` | `parse_edit_order` | `success` (logical), `order_id` (character), `errors` (collapsed character) |
| `preview_edit_order()` | `parse_edit_preview` | `errors` (collapsed character), then numerics `slippage`, `order_total`, `commission_total`, `quote_size`, `base_size`, `best_bid`, `average_filled_price` |
| `cancel_orders()` | `parse_cancel_results` | one row per order: `order_id` (character), `success` (logical), `failure_reason` (collapsed character) |

`edit_order()` / `preview_edit_order()` require at least one of `price`
or `size`. `cancel_orders()` takes a character vector of `order_ids`.

```{r edit-order}
trading$edit_order("1111aaaa-2222-bbbb-3333-cccccccccccc", price = 71000)[]
```

```{r preview-edit-order}
trading$preview_edit_order("1111aaaa-2222-bbbb-3333-cccccccccccc", price = 71000)[]
```

```{r cancel-orders}
trading$cancel_orders(c("1111aaaa-2222-bbbb-3333-cccccccccccc"))[]
```

---

## `CoinbaseFutures` — US futures (CFM)

All endpoints require credentials and a funded, approved CFM futures
account. Futures **orders are placed through the same order endpoint as
spot** — use `CoinbaseTrading$add_order()` with a futures `product_id`
(e.g. `"BIT-31OCT26-CDE"`) and a futures order configuration; this
class manages the surrounding account state only. Coinbase's INTX
perpetual endpoints (non-US) are intentionally not wrapped.

| Method | Endpoint | Shape |
|---|---|---|
| `get_balance_summary()` | `GET /api/v3/brokerage/cfm/balance_summary` | single row |
| `get_positions()` | `GET /api/v3/brokerage/cfm/positions` | one row per position |
| `get_position(product_id)` | `GET /api/v3/brokerage/cfm/positions/{id}` | single row |
| `schedule_sweep(usd_amount)` | `POST /api/v3/brokerage/cfm/sweeps/schedule` | single row |
| `get_sweeps()` | `GET /api/v3/brokerage/cfm/sweeps` | one row per sweep |
| `cancel_sweep()` | `DELETE /api/v3/brokerage/cfm/sweeps` | single row |
| `get_intraday_margin_setting()` | `GET /api/v3/brokerage/cfm/intraday/margin_setting` | single row |
| `set_intraday_margin_setting(setting)` | `POST /api/v3/brokerage/cfm/intraday/margin_setting` | single row (echoes `setting`) |
| `get_current_margin_window(margin_profile_type)` | `GET /api/v3/brokerage/cfm/intraday/current_margin_window` | single row |

```{r futures-init}
futures <- CoinbaseFutures$new()
```

```{r futures-init-hidden, echo = FALSE}
futures <- CoinbaseFutures$new(keys = KEYS)
```

### Balance summary

Parser `parse_futures_balance`. Every monetary field is a nested
`{value, currency}` object on the wire, flattened here to `numeric`
via `flex_num` (which accepts either a scalar or a `{value, currency}`
object). A single row:

| Column | Type |
|---|---|
| `futures_buying_power` | `numeric` |
| `total_usd_balance` | `numeric` |
| `cbi_usd_balance` | `numeric` |
| `cfm_usd_balance` | `numeric` |
| `total_open_orders_hold_amount` | `numeric` |
| `unrealized_pnl` | `numeric` |
| `daily_realized_pnl` | `numeric` |
| `initial_margin` | `numeric` |
| `available_margin` | `numeric` |
| `liquidation_threshold` | `numeric` |
| `liquidation_buffer_amount` | `numeric` |
| `liquidation_buffer_percentage` | `numeric` (plain scalar, not `{value, currency}`) |

```{r futures-balance}
futures$get_balance_summary()[]
```

### Positions

Parser `parse_futures_positions`, one row per open position:

| Column | Type |
|---|---|
| `product_id` | `character` |
| `side` | `character` |
| `number_of_contracts` | `numeric` (flattened) |
| `current_price` | `numeric` (flattened) |
| `avg_entry_price` | `numeric` (flattened) |
| `unrealized_pnl` | `numeric` (flattened) |
| `daily_realized_pnl` | `numeric` (flattened) |
| `expiration_time` | `POSIXct` (UTC) |

```{r futures-positions}
futures$get_positions()[]
```

### Sweeps

Parser `parse_futures_sweeps`, one row per sweep:

| Column | Type |
|---|---|
| `id` | `character` |
| `requested_amount` | `numeric` (flattened) |
| `should_sweep_all` | `logical` |
| `status` | `character` |
| `schedule_time` | `POSIXct` (UTC) |

```{r futures-sweeps}
futures$get_sweeps()[]
```

### Margin window and settings

`get_current_margin_window()` (parser `parse_margin_window`) flattens
the nested `margin_window` object into scalars — a single row with
`margin_window_type` (character), `end_time` (`POSIXct`),
`is_intraday_margin_killswitch_enabled` (logical), and
`is_intraday_margin_enrollment_killswitch_enabled` (logical). It
requires a `margin_profile_type` argument. `schedule_sweep()`,
`cancel_sweep()`, and `get_intraday_margin_setting()` go through the
generic `as_dt_row` flattener; `set_intraday_margin_setting()` returns
a single-row `data.table(setting = <applied value>)` because the
success body is empty.

```{r margin-window}
futures$get_current_margin_window("MARGIN_PROFILE_TYPE_RETAIL_INTRADAY_MARGIN_1")[]
futures$get_intraday_margin_setting()[]
```

---

## Standalone helpers

### Credentials and base URLs

```{r helpers-credentials}
adv_url <- get_base_url()              # api.coinbase.com (auth)
ex_url  <- get_exchange_base_url()     # api.exchange.coinbase.com (public)
c(advanced_trade = adv_url, exchange = ex_url)
```

`get_api_keys()` reads `COINBASE_API_KEY_NAME` / `COINBASE_API_PRIVATE_KEY`
from `.Renviron` (never run with real credentials in a document):

```{r helpers-keys, eval = FALSE}
keys <- get_api_keys()   # reads .Renviron
```

### Low-level HTTP

`coinbase_build_request()` constructs and JWT-signs every request. You
should rarely call it directly — every method goes through it — but it
is exported so you can wrap any not-yet-bound endpoint without
re-implementing ES256 / EdDSA signing.

### Bulk tick-history download

`coinbase_backfill_trades()` downloads deep tick history for many
products and writes the results to a CSV incrementally, so progress
survives an interruption. It writes to disk, so it is shown but not run
here:

```{r backfill, eval = FALSE}
box::use(coinbase[coinbase_backfill_trades], lubridate[ymd])

# Backfill deep tick history for many products, with CSV resume so an
# aborted run doesn't restart from scratch.
coinbase_backfill_trades(
  symbols = c("BTC-USD", "ETH-USD"),
  from    = ymd("2024-01-01"),
  to      = ymd("2024-02-01"),
  file    = "data/trades.csv"
)
```

### Tick aggregation: `trades_to_ohlcv()`

This is the deep-history path. Coinbase's `/candles` endpoint is
shallow, so complete OHLCV at any timeframe is built from ticks:
download trades, then aggregate. `trades_to_ohlcv()` takes a
`data.table` with `time` (`POSIXct`), `price` (`numeric`), and `size`
(`numeric`) columns — exactly what `get_trades()` /
`get_trades_history()` return — plus an `interval` in seconds, and
returns the canonical six-column OHLCV table:

| Column | Type | Notes |
|---|---|---|
| `datetime` | `POSIXct` (UTC) | floored bar start |
| `open` | `numeric` | first trade price in the bar |
| `high` | `numeric` | max trade price in the bar |
| `low` | `numeric` | min trade price in the bar |
| `close` | `numeric` | last trade price in the bar |
| `volume` | `numeric` | summed trade size |

Open/close are the first/last trade by time (`trade_id` breaks ties
within an identical timestamp when present); empty intervals produce no
row. The column layout matches `get_ohlcv()` exactly, so candle data
from either source is interchangeable.

```{r aggregate}
ticks <- market$get_trades("BTC-USD", limit = 1000L)
bars  <- trades_to_ohlcv(ticks, interval = 60)   # 1-minute bars
bars[, .(datetime, open, high, low, close, volume)]
```

### Symbol verification and client order IDs

```{r helpers-verify}
verify_symbol("BTC-USD")          # TRUE
verify_symbol("BIT-28FEB25-CDE")  # TRUE  (multi-segment expiring future)
verify_symbol("BTCUSD")           # FALSE (no dash separator)

generate_client_order_id()        # fresh RFC-4122 v4 UUID
```

### Async usage

Pass `async = TRUE` to any class constructor; methods then return
promises. Drive them with the `coro::async()` / `await()` idiom and
drain the `later` event loop. No pipes anywhere.

```{r async}
box::use(
  coro[async, await],
  later
)

market_async <- CoinbaseMarketData$new(async = TRUE)
results <- NULL

main <- async(function() {
  ticker  <- await(market_async$get_ticker("BTC-USD"))
  candles <- await(market_async$get_ohlcv("BTC-USD", granularity = "1min"))
  results <<- list(ticker = ticker, candles = candles)
  return(invisible(NULL))
})

main()
while (!later$loop_empty()) later$run_now()

results$ticker[]
results$candles[]
```

See `vignette("async-usage", package = "coinbase")` for the full
pattern.

---

# Data-shape conventions

Now that you've seen the surface, here are the rules used to decide
what a row in the returned `data.table` represents.

Every method follows one principle:

> **Identify the entity for the endpoint, and return one row per
> entity.**

A trade gets a row. An order gets a row. An account balance gets a
row. A candle gets a row. Anything nested *under* the entity becomes a
flat column on the same row or an additional row on a different axis —
**never a list column**.

The overriding invariant on `coinbase` is the no-list-column contract.
Even the generic flatteners (`as_dt_row` / `as_dt_list`) enforce it:
any nested object, array, or multi-element value that doesn't have a
hand-written parser is collapsed to a single JSON string rather than
left as a list cell. There are four treatments.

## Treatment A — Flatten `{value, currency}` amounts to numerics

Coinbase represents monetary amounts as nested `{value, currency}`
objects on the wire. Every such field is flattened to its numeric
`value` (helpers `amount_value` / `flex_num`), dropping the currency
tag — the currency is already implied by the column or by a sibling
`currency` column.

```{r treatment-a}
accts <- account$get_accounts()
accts$available_balance     # numeric, not list({value=..., currency=...})

bal <- futures$get_balance_summary()
bal$futures_buying_power    # numeric, flattened from {value, currency}
```

Where it's used: `available_balance` / `hold` on accounts; every
amount on the futures balance summary, positions, and sweeps
(`futures_buying_power`, `unrealized_pnl`, `current_price`,
`avg_entry_price`, `requested_amount`, …). `flex_num` is the lenient
variant — it accepts either a bare scalar or a `{value, currency}`
object — because some futures fields arrive in either form depending
on the account state.

## Treatment B — Long format for arrays of objects

When an array's elements are themselves records (each has a `price`, a
`size`, a `side`, …), explode to one row per element with a `side` or
position column where order matters. On `coinbase` this applies to
exactly one endpoint: the order book.

```{r treatment-b}
ob <- market$get_orderbook("BTC-USD", level = 2L)
ob[, .(side, price, size, num_orders)]
```

The `bids` and `asks` arrays are stacked with a `side` discriminator.
The level-3 distinction is the subtle part: at levels 1-2 the third
element is an order **count** (`num_orders`, numeric); at level 3 the
book is non-aggregated and the third element is an **`order_id`**
string, so the parser emits a character `order_id` column instead.
Check which you got with `"order_id" %in% names(ob)`.

## Treatment C — Flatten fixed-schema nested objects to scalar columns

When the nested data is an *object* (not an array) with a known fixed
key set, flatten the inner fields into scalar columns on the same row.
The entity stays one row.

```{r treatment-c}
fees <- account$get_fees()
fees$maker_fee_rate   # was nested under fee_tier
fees$pricing_tier     # was nested under fee_tier

orders <- trading$get_orders(product_ids = "BTC-USD")
orders$config_type    # the order_configuration's one key
orders$limit_price    # was nested inside order_configuration
```

Where it's used: `fee_tier` on `get_fees`
(`pricing_tier` / `maker_fee_rate` / `taker_fee_rate` / `usd_from` /
`usd_to`); `order_configuration` on orders, create-order, and
preview (`config_type`, `base_size`, `quote_size`, `limit_price`,
`stop_price`, `stop_trigger_price`, `stop_direction`, `end_time`,
`post_only` — see `flatten_order_config`); `margin_window` on
`get_current_margin_window`. The detailed-type key of
`order_configuration` is surfaced as the `config_type` column, distinct
from the coarse `order_type` enum.

## Treatment D — Collapse error arrays to one string

Coinbase returns validation / preview / edit errors as an array whose
elements are sometimes objects and sometimes bare strings, and whose
reason lives under different keys per endpoint (`error_code`,
`new_order_failure_reason`, `preview_failure_reason`,
`edit_failure_reason`, `failure_reason`, `error`, `message`, …). Rather
than leave a list column, `collapse_errors` looks each element up by
its known keys and joins the array into a single `"; "`-separated
character string — `NA_character_` when there are no errors.

```{r treatment-d}
pv <- trading$preview_order(
  "BTC-USD", "BUY",
  list(market_market_ioc = list(quote_size = "10"))
)
pv$errs   # one string, or NA when the preview validated cleanly
```

Where it's used: `errs` on `preview_order`; `failure_reason` on
`add_order` and `cancel_orders`; `errors` on `edit_order` and
`preview_edit_order`.

## The generic fallback

Methods without a hand-written parser (`get_products`, `get_product`,
`get_ticker`, `get_portfolios`, `get_key_permissions`,
`get_server_time`, `schedule_sweep`, `cancel_sweep`,
`get_intraday_margin_setting`) go through `as_dt_row` / `as_dt_list`.
These flatten every scalar field into a column and, crucially, collapse
any unexpected nested object/array or multi-element value to a single
JSON string — so even an endpoint the package doesn't model in detail
still returns a list-column-free table. Recover such a field with
`jsonlite::fromJSON()` if you ever need its structure.

## Two cross-cutting rules

These apply to every treatment, regardless of method.

1. **Empty / null field → scalar `NA` (typed), not a list cell.** A
   missing balance is `NA_real_`, a missing timestamp is `NA`
   (`POSIXct`), a missing string is `NA_character_`. Downstream
   `is.na()` keeps working; no list-column gymnastics.
2. **Empty response → empty `data.table`.** No synthetic stub rows.
   `get_trades()` with nothing to return, `cancel_orders()` whose
   batch matched nothing, `get_positions()` with no open positions —
   all return a zero-row table. `nrow()` is the honest count of
   "things I got back," and the absence of an error is the success
   signal.

## What was *not* done

A few intentional non-goals, shared with the sister `alpaca`,
`binance`, and `kucoin` packages:

- **No list columns, ever.** This is the headline guarantee. Nested
  `{value, currency}` amounts are flattened to numerics, fixed-schema
  objects to scalar columns, error arrays to a single string, and any
  unmodelled nesting to a JSON string. A returned table never hides a
  list cell.
- **No automatic local-time conversion.** Timestamps come back as UTC
  `POSIXct`. Convert with `format(x, tz = "America/New_York")` or
  similar at display time.
- **`client_order_id` is round-tripped verbatim.** Whatever string you
  pass (or the UUID `generate_client_order_id()` mints) goes back to
  you unchanged.
- **No client-side rate-limiting.** The package surfaces Coinbase's
  rate-limit errors but does not back off on its own — that is the
  caller's job.
- **No reconnect / retry on transient network errors.** The single
  call is what you asked for; wrap with `httr2::req_retry()` (passed
  through `coinbase_build_request()`) if you want retries.

## Why this matters across exchanges

The `alpaca`, `binance`, `kucoin`, and `coinbase` packages all follow
the same shape rule. Once you've learned `data.table` idioms for one
of them, the same idioms work on the others — pivot a portfolio's
balances across multiple exchanges with a straight `rbindlist` plus an
`exchange` column, no per-source shape massage and no escape hatch into
`lapply` over hidden lists.

```{r ledger}
# Combine spot accounts + futures balance into one ledger
ledger <- data.table::rbindlist(
  list(
    account$get_accounts()[, wallet := "spot"],
    futures$get_balance_summary()[, wallet := "futures"]
  ),
  use.names = TRUE,
  fill = TRUE
)
ledger[, .(wallet, currency, available_balance, futures_buying_power)]
```

The same predictability is what makes the connector layer (`exchanges`
package, on top of `tradebot-core`) easy to write: each raw wrapper
returns data the connector can re-shape without special-casing list
columns or unwrapping nested structures.

## See also

- `vignette("getting-started", package = "coinbase")` — guided walk
  through fetching market data, placing a preview order, and querying
  balances.
- `vignette("async-usage", package = "coinbase")` — using the same
  methods with `async = TRUE`.
- The sister `alpaca`, `binance`, and `kucoin` packages — the same
  convention applied to other exchanges, with the same Package Tour
  layout.
```
