---
title: "Shorting with US Futures (CFM) with coinbase"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shorting with US Futures (CFM) with coinbase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

# This vignette renders against a mock HTTP router so it prints realistic,
# deterministic data with no network, no real credentials, and no funds.
# httr2's native global mock hook intercepts every request; coinbase still
# signs a JWT before the request fires, so we hand it a THROWAWAY, ephemeral
# EC P-256 key generated fresh at build time. It signs fine, the mock ignores
# the Authorization header, and it grants nothing.
box::use(
  coinbase[
    CoinbaseTrading, CoinbaseFutures, CoinbaseMarketData
  ],
  connectcore[local_mock_api],
  ../tests/testthat/mock_router[.mock_routes]
)

local_mock_api(.mock_routes)

.sk <- openssl::ec_keygen("P-256")
KEYS <- list(
  api_key_name = "organizations/00000000-0000-0000-0000-000000000000/apiKeys/00000000-0000-0000-0000-000000000000",
  api_private_key = openssl::write_pem(.sk)
)
```

This vignette covers going **short** through Coinbase Financial Markets (CFM)
US futures using the `coinbase` package. Coinbase spot is long-only — you
cannot sell a coin you do not hold — so the headline route to a short position
for a US customer is a `SELL` order on a CFM futures contract. Unlike crypto
exchanges that expose a separate futures order endpoint, Coinbase places
**futures orders through the same order endpoint as spot**: you submit them with
`CoinbaseTrading$add_order()` using a futures `product_id`. The
`CoinbaseFutures` class manages the surrounding account state — balances,
positions, cash sweeps, and intraday margin.

> **Disclaimer — leverage and liquidation risk.** Futures are leveraged
> instruments. A short position has theoretically unbounded loss: if the
> underlying rises, your loss grows without limit, and the position can be
> **liquidated** the moment your equity falls below the maintenance threshold,
> crystallising losses that may exceed your initial margin. Funding, fees, and
> contract expiry add further risk. Every order below is shown as a **dry-run
> preview** — nothing here ever transmits a live order. Trade futures only with
> risk capital you can afford to lose, and never run a live order example
> without understanding it fully.

## Why CFM futures for shorting

| Venue | Direction | Wrapped here? |
|-------|-----------|---------------|
| Coinbase spot (CBI) | Long only | Yes (`CoinbaseTrading`, spot `product_id`) |
| CFM US futures | Long **and short** | Yes (orders via `CoinbaseTrading`; account via `CoinbaseFutures`) |
| INTX perpetuals (`/intx/*`) | Long and short | No — non-US jurisdictions only, intentionally excluded |

US customers trade the CFM futures covered by this package. Coinbase's INTX
perpetual-futures endpoints are for eligible non-US jurisdictions and are not
wrapped. To open a short, you submit a `SELL` order on a CFM futures product
(an expiring contract such as a nano-BTC future); `CoinbaseFutures` then reports
the resulting position, margin, and PnL.

This complements the `alpaca` package, which trades long US equities: holding
long stocks in `alpaca` while shorting a correlated crypto future on CFM is the
building block of a pairs / statistical-arbitrage strategy spanning the two
brokers.

## Setup

Credentials come from the Coinbase Developer Platform (a JSON file with a
`name` and a `privateKey`). Store them in `.Renviron` as
`COINBASE_API_KEY_NAME` and `COINBASE_API_PRIVATE_KEY`; the multi-line
`privateKey` is placed on one line with its newlines escaped as the two
characters `\n`, which `get_api_keys()` unescapes before signing. The CFM
futures account also requires separate approval and funding on Coinbase.

```bash
# In ~/.Renviron (these are obviously-fake placeholders — never commit real keys):
COINBASE_API_KEY_NAME="organizations/<org-uuid>/apiKeys/<key-uuid>"
COINBASE_API_PRIVATE_KEY="-----BEGIN EC PRIVATE KEY-----\n<fake-key-body>\n-----END EC PRIVATE KEY-----\n"
```

With those set, `get_api_keys()` reads them with no arguments, so you simply
construct each client and the credentials are picked up automatically. Public
market data needs no credentials at all.

```{r load, eval = FALSE}
box::use(
  coinbase[
    CoinbaseTrading, CoinbaseFutures, CoinbaseMarketData, get_api_keys
  ]
)

keys <- get_api_keys()

market <- CoinbaseMarketData$new()
trading <- CoinbaseTrading$new(keys = keys)
futures <- CoinbaseFutures$new(keys = keys)
```

```{r load-hidden, echo = FALSE}
# Build the clients against the mock with a throwaway key so the authenticated
# calls below sign and execute.
market <- CoinbaseMarketData$new()
trading <- CoinbaseTrading$new(keys = KEYS)
futures <- CoinbaseFutures$new(keys = KEYS)
```

---

## CFM Futures Account State

`CoinbaseFutures` manages everything around the position. It does **not** place
orders itself — orders go through `CoinbaseTrading` (see below).

### Balance Summary

The balance summary is the first thing to check before shorting: it reports your
futures buying power, the margin already committed, unrealised PnL, and — most
importantly — your liquidation threshold and buffer.

```{r balance-summary}
summary <- futures$get_balance_summary()
summary[, .(
  futures_buying_power,        # buying power available for futures orders
  cfm_usd_balance,             # USD held in the CFM (futures) account
  cbi_usd_balance,             # USD held in the spot (CBI) account
  initial_margin,              # margin committed to open positions
  available_margin,            # margin still free
  unrealized_pnl,              # mark-to-market PnL on open positions
  liquidation_threshold,       # equity level at which positions are liquidated
  liquidation_buffer_amount,   # cushion above the threshold
  liquidation_buffer_percentage
)]
```

### Open Positions

`get_positions()` returns every open CFM position; a short shows `side` of
`"SHORT"` with negative unrealised PnL when the contract price rises.

```{r positions}
positions <- futures$get_positions()
positions[, .(
  product_id, side, number_of_contracts,
  avg_entry_price, current_price,
  unrealized_pnl, daily_realized_pnl, expiration_time
)]
```

Query a single contract by its product ID:

```{r position}
pos <- futures$get_position(product_id = "BIT-31OCT26-CDE")
pos[, .(product_id, side, number_of_contracts, avg_entry_price, unrealized_pnl)]
```

### Cash Sweeps (CFM <-> Spot)

Cash moves between the spot (CBI) wallet and the futures (CFM) account through
scheduled sweeps. Schedule a sweep of USD from futures back to spot, list
pending sweeps, and cancel the pending sweep:

```{r sweeps}
# Schedule a sweep of $100 from the CFM futures account to the spot USD wallet
scheduled <- futures$schedule_sweep(usd_amount = 100)
scheduled[]

# List scheduled and pending sweeps
sweeps <- futures$get_sweeps()
sweeps[, .(id, requested_amount, should_sweep_all, status, schedule_time)]

# Cancel the pending sweep
futures$cancel_sweep()[]
```

### Intraday Margin

Read and set your intraday margin setting. Intraday margin lowers the margin
requirement during the trading session (raising effective leverage, and risk);
the standard setting applies the full requirement.

```{r margin-setting}
# Current setting
futures$get_intraday_margin_setting()[]

# Switch to intraday margin (raises leverage and liquidation risk)
futures$set_intraday_margin_setting(setting = "INTRADAY_MARGIN_SETTING_INTRADAY")[]

# Switch back to the standard (full) margin requirement
futures$set_intraday_margin_setting(setting = "INTRADAY_MARGIN_SETTING_STANDARD")[]
```

Check the current margin window — whether intraday margin is presently active
and when it ends. The killswitch flags indicate whether Coinbase has disabled
intraday margin or new enrollment:

```{r margin-window}
window <- futures$get_current_margin_window(
  margin_profile_type = "MARGIN_PROFILE_TYPE_RETAIL_INTRADAY_MARGIN_1"
)
window[, .(
  margin_window_type, end_time,
  is_intraday_margin_killswitch_enabled,
  is_intraday_margin_enrollment_killswitch_enabled
)]
```

---

## Finding a Futures Product

Futures products appear in the same product catalogue as spot. List the
products and pick out the expiring CFM contracts — their IDs carry an expiry
(e.g. `BIT-31OCT26-CDE`):

```{r products}
products <- market$get_products()
products[, .(id, status)]
```

Inspect a single contract's metadata before trading it. The same `get_product()`
call works for an expiring CFM contract by passing its futures `product_id`:

```{r product, eval = FALSE}
contract <- market$get_product(product_id = "BIT-31OCT26-CDE")
contract[]
```

---

## Opening a Short (Preview Only)

A short is simply a **`SELL` order on a futures `product_id`**, placed through
`CoinbaseTrading$add_order()` — the very same method used for spot. The order
configuration follows the standard one-key form
(`market_market_ioc`, `limit_limit_gtc`, etc.), where the key names the detailed
order type and the inner list carries the sizes/prices.

**We will not place a live short here.** Use `preview_order()` first: it is a
dry run that validates the configuration and returns the estimated total,
commission, sizes, and any errors — and **places nothing**.

### Preview a Market Short

```{r preview-market-short}
preview <- trading$preview_order(
  product_id = "BIT-31OCT26-CDE",
  side = "SELL",                                    # SELL on a future = open short
  order_configuration = list(
    market_market_ioc = list(base_size = "1")       # 1 contract
  )
)
preview[, .(order_total, commission_total, base_size, best_bid, best_ask, slippage, errs)]
```

### Preview a Limit Short with Leverage and Margin Type

`add_order()` and `preview_order()` accept `leverage`, `margin_type`
(`"CROSS"` or `"ISOLATED"`), and `retail_portfolio_id`. Higher leverage means a
closer liquidation threshold — preview the numbers before committing:

```{r preview-limit-short}
preview <- trading$preview_order(
  product_id = "BIT-31OCT26-CDE",
  side = "SELL",
  order_configuration = list(
    limit_limit_gtc = list(
      base_size = "1",
      limit_price = "95000"
    )
  ),
  leverage = "2",
  margin_type = "CROSS"
)
preview[, .(order_total, commission_total, base_size, best_bid, best_ask, errs, preview_id)]
```

### Placing the Live Short (Use With Extreme Caution)

Only when the preview is satisfactory would you place the live order. This is a
real, leveraged, short position — it can be liquidated. The example is left
`eval = FALSE` and shown purely for completeness:

```{r live-short, eval = FALSE}
order <- trading$add_order(
  product_id = "BIT-31OCT26-CDE",
  side = "SELL",
  order_configuration = list(
    limit_limit_gtc = list(
      base_size = "1",
      limit_price = "95000"
    )
  ),
  leverage = "2",
  margin_type = "CROSS"
)
order[, .(success, order_id, product_id, side, failure_reason)]
```

`add_order()` also accepts `self_trade_prevention_id` (preview does not) and a
`client_order_id` idempotency key, which defaults to a fresh UUID via
`generate_client_order_id()`.

---

## Managing the Short

### Inspect Open Futures Orders

`get_orders()` filters historical orders; pass `product_type = "FUTURE"` to
scope to futures and `order_side = "SELL"` for the short legs:

```{r futures-orders}
open_shorts <- trading$get_orders(
  product_type = "FUTURE",
  order_side = "SELL",
  order_status = "OPEN",
  limit = 50
)
open_shorts[, .(order_id, product_id, side, status, base_size, limit_price, created_time)]
```

### Fills

`get_fills()` reports executions. Filter by `order_ids` (plural), `trade_ids`,
or `product_ids`:

```{r futures-fills}
fills <- trading$get_fills(
  product_ids = "BIT-31OCT26-CDE",
  sort_by = "TRADE_TIME"
)
fills[, .(trade_id, order_id, product_id, side, price, size, commission, trade_time)]
```

### Edit or Cancel

Reprice or resize an open short, or cancel it outright:

```{r edit-cancel}
# Move the limit short to a new price
trading$edit_order(order_id = "1111aaaa-2222-bbbb-3333-cccccccccccc", price = 96000)

# Cancel one or more orders
trading$cancel_orders(order_ids = "1111aaaa-2222-bbbb-3333-cccccccccccc")
```

### Closing the Short

The idiomatic way to flatten a position is `close_position()`, which submits the
offsetting order for you. Pass the futures `product_id`, and optionally a `size`
to close only part of the position (omit `size` to close all of it):

```{r close-position}
closed <- trading$close_position(product_id = "BIT-31OCT26-CDE", size = "1")
closed[, .(success, order_id, product_id, side)]
```

You can also close manually by submitting the opposite side — a `BUY` order on
the same futures product, for the same number of contracts. Preview it first:

```{r preview-close}
preview <- trading$preview_order(
  product_id = "BIT-31OCT26-CDE",
  side = "BUY",                                     # BUY closes (covers) the short
  order_configuration = list(
    market_market_ioc = list(base_size = "1")
  )
)
preview[, .(order_total, commission_total, base_size, errs)]
```

---

## Pairs Trading with alpaca

A common use of this short leg is a market-neutral pair: hold a long US-equity
position in `alpaca` and short a correlated crypto future on CFM. The two
brokers are driven independently — `alpaca` for the long stock leg, `coinbase`
for the short futures leg — and each reports its own positions and PnL:

```{r pairs}
# Long leg (alpaca): buy the equity
# alpaca_trading$add_order(symbol = "COIN", side = "buy", type = "market",
#   time_in_force = "day", qty = 100)

# Short leg (coinbase CFM): preview the offsetting futures short
trading$preview_order(
  product_id = "BIT-31OCT26-CDE",
  side = "SELL",
  order_configuration = list(market_market_ioc = list(base_size = "1"))
)[, .(order_total, commission_total, base_size, errs)]
```

Monitor both legs' exposure: the equity position via `alpaca`'s account
methods, and the futures short via `futures$get_positions()` and
`futures$get_balance_summary()`.

---

## Async Usage

Every method runs asynchronously when the client is constructed with
`async = TRUE`, returning a promise. Consume promises with `coro::async()` and
`await()`, and drain the event loop yourself — without any pipe operator:

```{r async-visible, eval = FALSE}
box::use(coro[async, await], later)

futures_async <- CoinbaseFutures$new(keys = keys, async = TRUE)
```

```{r async-hidden, echo = FALSE}
box::use(coro[async, await], later)

futures_async <- CoinbaseFutures$new(keys = KEYS, async = TRUE)
```

```{r async}
run <- async(function() {
  summary <- await(futures_async$get_balance_summary())
  positions <- await(futures_async$get_positions())
  print(summary[, .(futures_buying_power, available_margin, liquidation_threshold)])
  print(positions[, .(product_id, side, number_of_contracts, unrealized_pnl)])
  return(invisible(NULL))
})

run()

# Drive the event loop until the promise settles
while (!later$loop_empty()) {
  later$run_now()
}
```

---

## Method Reference

### CoinbaseFutures

| Method | Description |
|--------|-------------|
| `get_balance_summary()` | Buying power, margin, unrealised PnL, liquidation thresholds |
| `get_positions()` | All open CFM futures positions |
| `get_position(product_id)` | A single position by product |
| `schedule_sweep(usd_amount)` | Schedule a cash sweep from CFM to spot |
| `get_sweeps()` | Scheduled and pending sweeps |
| `cancel_sweep()` | Cancel the pending sweep |
| `get_intraday_margin_setting()` | Current intraday margin setting |
| `set_intraday_margin_setting(setting)` | Set intraday/standard margin |
| `get_current_margin_window(margin_profile_type)` | Current margin window and killswitch flags |

### CoinbaseTrading (used for futures orders)

| Method | Description |
|--------|-------------|
| `add_order(product_id, side, order_configuration, ...)` | Place an order; `SELL` on a future opens a short. Accepts `leverage`, `margin_type`, `self_trade_prevention_id`, `retail_portfolio_id`, `client_order_id` |
| `preview_order(product_id, side, order_configuration, ...)` | Dry-run validation; places nothing. Accepts `leverage`, `margin_type`, `retail_portfolio_id` |
| `get_order(order_id)` | A single order by ID |
| `get_orders(...)` | Historical orders; filter by `product_type`, `order_side`, `order_status`, `order_ids`, `start_date`, `end_date`, `order_types`, `sort_by`, ... |
| `get_fills(...)` | Historical fills; filter by `order_ids`, `trade_ids`, `product_ids`, sequence-timestamp bounds, `sort_by` |
| `edit_order(order_id, price, size)` | Reprice/resize an open order |
| `preview_edit_order(order_id, price, size)` | Dry-run an edit |
| `cancel_orders(order_ids)` | Cancel one or more orders |

## Next Steps

- See `vignette("getting-started")` for basic market data and order placement.
- See `vignette("data-shapes")` for the exact columns each call returns.
- Consult the [Coinbase Advanced Trade API documentation](https://docs.cdp.coinbase.com/advanced-trade/docs/welcome)
  for full endpoint details and the current CFM contract universe.
