---
title: "Getting Started with coinbase"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with coinbase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

# This vignette renders against a global httr2 mock: every request is answered
# from canned fixtures, so the examples execute and print realistic,
# deterministic data with no network, no real credentials, and no funds.
box::use(
  coinbase[
    CoinbaseMarketData, CoinbaseAccount, CoinbaseTrading,
    trades_to_ohlcv, coinbase_backfill_trades, get_api_keys
  ],
  coro,
  later,
  ../tests/testthat/mock_router[mock_router]
)

options(httr2_mock = mock_router)

# coinbase signs a JWT with the private key BEFORE the request is performed, so
# a loadable key must exist even though the mock ignores the Authorization
# header. Generate a throwaway ephemeral EC P-256 key for this build: it signs
# fine, grants nothing, and is regenerated each render.
.sk <- openssl::ec_keygen("P-256")
KEYS <- list(
  api_key_name = "organizations/00000000-0000-0000-0000-000000000000/apiKeys/00000000-0000-0000-0000-000000000000",
  api_private_key = openssl::write_pem(.sk)
)
```

This vignette demonstrates how to use `coinbase` in **synchronous** mode to
retrieve public market data, read authenticated account state, and safely
*preview* orders against the Coinbase Advanced Trade API.

## Disclaimer

This software is provided for educational and research purposes. Trading
cryptocurrency carries substantial risk and you are solely responsible for any
orders placed through this package. Every example that could move money is shown
as a `preview_order()` dry run (which executes nothing); the one live
`add_order()` call is left commented out. Validate with a preview before
submitting anything live.

## Installation

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("dereckscompany/coinbase")
```

## Setup

Public market data needs no credentials. Authenticated endpoints (accounts,
fees, trading) require a Coinbase Developer Platform (CDP) API key. Create one
at <https://www.coinbase.com/settings/api> and download the JSON file, which
contains a `name` and a `privateKey`.

Store the credentials as environment variables in `.Renviron`. The downloaded
`privateKey` is multi-line PEM; to keep it on a single line, escape its newlines
as the two characters `\n` (`get_api_keys()` unescapes them back before use).
Both EC keys (`-----BEGIN EC PRIVATE KEY-----`, signed with ES256) and
base64-encoded Ed25519 keys (signed with EdDSA) are supported.

```bash
COINBASE_API_KEY_NAME="organizations/<org-uuid>/apiKeys/<key-uuid>"
COINBASE_API_PRIVATE_KEY="-----BEGIN EC PRIVATE KEY-----\n<fake-key-body>\n-----END EC PRIVATE KEY-----\n"
```

> **Two hosts.** Coinbase splits across two hosts. Authenticated trading and
> account endpoints use the Advanced Trade host (`https://api.coinbase.com`,
> `get_base_url()`); the public market-data endpoints with deep history use the
> Exchange host (`https://api.exchange.coinbase.com`, `get_exchange_base_url()`).
> Each class selects the correct host per request, so you rarely set these by
> hand.

```{r load, eval = FALSE}
box::use(
  coinbase[
    CoinbaseMarketData, CoinbaseAccount, CoinbaseTrading,
    trades_to_ohlcv, coinbase_backfill_trades, get_api_keys
  ]
)

keys <- get_api_keys(
  api_key_name = "organizations/<org-uuid>/apiKeys/<key-uuid>",
  api_private_key = "-----BEGIN EC PRIVATE KEY-----\n<fake-key-body>\n-----END EC PRIVATE KEY-----\n"
)
```

When the environment variables are set, `get_api_keys()` reads them with no
arguments, so in practice you simply call `CoinbaseAccount$new()` and the
credentials are picked up automatically.

---

## Market Data

The `CoinbaseMarketData` class covers all public (no auth) market endpoints. It
talks to the Exchange host, which exposes deep trade history.

```{r market-init}
market <- CoinbaseMarketData$new()
```

### Products

List every available trading product (currency pair):

```{r products}
products <- market$get_products()
products[]
```

### Ticker

Best bid/ask and the last trade for a single product:

```{r ticker}
ticker <- market$get_ticker(product_id = "BTC-USD")
ticker[]
```

### OHLCV Candles

The `/candles` endpoint returns roughly 300 bars per call, so it is a
convenience for recent data. Valid granularities are `"1min"`, `"5min"`,
`"15min"`, `"1hour"`, `"6hour"`, and `"1day"`. The result has columns
`datetime`, `open`, `high`, `low`, `close`, `volume`:

```{r ohlcv}
candles <- market$get_ohlcv(product_id = "BTC-USD", granularity = "1min")
candles[]
```

### Recent Trades

Recent tick trades, with columns `trade_id`, `side`, `price`, `size`, `time`:

```{r trades}
trades <- market$get_trades(product_id = "BTC-USD", limit = 100)
trades[]
```

### Order Book

A snapshot at level `1` (best bid/ask), `2` (top 50 aggregated), or `3` (full,
non-aggregated). The result is a long table with a `side` column:

```{r orderbook}
book <- market$get_orderbook(product_id = "BTC-USD", level = 2)
book[]
```

### Server Time

```{r server-time}
st <- market$get_server_time()
st[]
```

### Market Stats (Scanner Source)

`get_stats()` returns 24-hour and 30-day stats for **every** product in a single
call -- the basis for a market scanner. Rank the returned table yourself, e.g. by
`volume` for the most active products or by 24h change `(last - open) / open` for
the top movers:

```{r stats}
stats <- market$get_stats()

# Most active products by 24h volume
head(stats[order(-volume)], 5)

# Biggest 24h gainers
stats[, change := (last - open) / open]
head(stats[order(-change)], 5)
```

For a single product, `get_product_stats()` also carries the RFQ/conversion
volumes:

```{r product-stats}
market$get_product_stats("BTC-USD")[]
```

### Best Bid/Ask Across Products

`get_best_bid_ask()` returns the top of book for many products in one call.
Unlike the other `CoinbaseMarketData` methods it uses the Advanced Trade host, so
it **requires credentials**:

```{r best-bid-ask}
market_auth <- CoinbaseMarketData$new()
```

```{r best-bid-ask-hidden, echo = FALSE}
market_auth <- CoinbaseMarketData$new(keys = KEYS)
```

```{r best-bid-ask-call}
market_auth$get_best_bid_ask(c("BTC-USD", "ETH-USD"))[]
```

---

## Deep Tick History and OHLCV

Coinbase's candle endpoint is shallow, so complete OHLCV at any timeframe is
built from ticks. `get_trades_history()` pages the trades endpoint backwards
from the most recent trade toward `start`, deduplicates, and returns the trades
sorted ascending by `time`:

```{r trades-history}
ticks <- market$get_trades_history(
  product_id = "BTC-USD",
  start = lubridate::as_datetime("2026-05-31 00:00:00", tz = "UTC"),
  end = lubridate::as_datetime("2026-05-31 06:00:00", tz = "UTC")
)
ticks[]
```

> **Note:** Tick volume is large. Bound the window with `start`/`end`, and use
> `max_pages` to cap how far back paging walks (each page is up to 1000 trades).

Aggregate those ticks into OHLCV bars at any interval (in seconds) with
`trades_to_ohlcv()`. The result mirrors `get_ohlcv()`: `datetime`, `open`,
`high`, `low`, `close`, `volume`:

```{r aggregate}
bars <- trades_to_ohlcv(ticks, interval = 60)
bars[]
```

---

## Bulk Backfill (Data Collection)

`coinbase_backfill_trades()` is the data-collection workflow: it downloads deep
tick history for one or more products and writes the results to a CSV
incrementally, so progress survives an interruption. Re-running the same call
resumes each product from its last recorded trade.

It writes a file to disk, so it is shown here but not executed:

```{r backfill, eval = FALSE}
coinbase_backfill_trades(
  symbols = c("BTC-USD", "ETH-USD"),
  from = lubridate::as_datetime("2026-05-01", tz = "UTC"),
  to = lubridate::as_datetime("2026-05-30", tz = "UTC"),
  file = "trades.csv"
)

# Resume an interrupted backfill -- just run the same call again. It reads the
# existing CSV and continues each symbol from its last stored trade.
```

The function returns the file path invisibly. If any symbols failed, a
`"failures"` attribute is attached: a `data.table` with `symbol` and `error`
columns. Once the CSV is collected, read it back and aggregate to OHLCV with
`trades_to_ohlcv()`.

---

## Account Information

The `CoinbaseAccount` class reads authenticated account state from the Advanced
Trade host. All endpoints require credentials.

```{r account-init}
account <- CoinbaseAccount$new()
```

```{r account-init-hidden, echo = FALSE}
account <- CoinbaseAccount$new(keys = KEYS)
```

### Balances

`get_accounts()` walks Coinbase's cursor pagination to return every account.
Balances arrive as numeric columns (`available_balance`, `hold`), never nested
objects:

```{r accounts}
accounts <- account$get_accounts()
accounts[, .(uuid, currency, available_balance, hold, type)]
```

### Fee Tier

`get_fees()` returns the transaction summary, including the current maker/taker
fee tier:

```{r fees}
fees <- account$get_fees()
fees[, .(pricing_tier, maker_fee_rate, taker_fee_rate, total_volume)]
```

### Key Permissions

Confirm what the calling API key is allowed to do:

```{r permissions}
perms <- account$get_key_permissions()
perms[]
```

### Portfolios

`get_portfolios()` lists your portfolios. For one portfolio,
`get_portfolio_breakdown()` returns its positions (spot, futures, and perpetual)
stacked into one `data.table`, tagged with `position_type`, and
`get_portfolio_summary()` returns the portfolio's aggregate totals as a separate
one-row `data.table` (both read the same endpoint):

```{r portfolios}
ports <- account$get_portfolios()
ports[]
```

```{r portfolio-breakdown}
bd <- account$get_portfolio_breakdown(ports$uuid[1])
bd[, .(position_type, product_id, asset, side, entry_price, mark_price, unrealized_pnl)]

# Portfolio-level totals come from a separate one-row table
account$get_portfolio_summary(ports$uuid[1])[]
```

---

## Trading

The `CoinbaseTrading` class places, previews, edits, cancels, and queries orders
and fills. All endpoints require credentials.

```{r trading-init}
trading <- CoinbaseTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- CoinbaseTrading$new(keys = KEYS)
```

### Order Configuration

Orders carry an `order_configuration`: a one-key named list whose key names the
detailed order type. Common shapes:

```{r order-config}
# Market buy of $10 (quote-denominated)
market_cfg <- list(market_market_ioc = list(quote_size = "10"))

# Limit buy of 0.001 BTC at 50000, good-till-cancelled
limit_cfg <- list(
  limit_limit_gtc = list(base_size = "0.001", limit_price = "50000")
)
```

### Preview an Order (Safe Dry Run)

`preview_order()` validates an order **without placing it** — it executes
nothing. It returns the estimated `order_total`, `commission_total`, sizes,
`best_bid`/`best_ask`, `slippage`, any validation `errs`, and a `preview_id`.
Always preview before submitting a live order:

```{r preview-order}
preview <- trading$preview_order(
  product_id = "BTC-USD",
  side = "BUY",
  order_configuration = market_cfg
)
preview[, .(order_total, commission_total, base_size, best_ask, errs)]
```

`preview_order()` also accepts the optional `leverage`, `margin_type`
(`"CROSS"` or `"ISOLATED"`), and `retail_portfolio_id` arguments.

### Place an Order

`add_order()` submits a live order that may execute. It mirrors
`preview_order()` and additionally accepts `client_order_id` (an idempotency
key, defaulting to a fresh UUID) and `self_trade_prevention_id`. The call below
runs against the mock; against the live API it would place a real order, so
preview first:

```{r add-order}
order <- trading$add_order(
  product_id = "BTC-USD",
  side = "BUY",
  order_configuration = limit_cfg
)
order[, .(success, order_id, product_id, side)]
```

### Edit an Order

`preview_edit_order()` is a dry run for an edit (it changes nothing), and
`edit_order()` applies a new price and/or size to an open order:

```{r edit-order}
edit_preview <- trading$preview_edit_order(
  order_id = order$order_id,
  price = "71000"
)
edit_preview[, .(order_total, commission_total, slippage)]

edited <- trading$edit_order(order_id = order$order_id, price = "71000")
edited[, .(success, order_id)]
```

### Query Orders

`get_orders()` retrieves historical orders, paginating over the cursor. It
accepts a rich set of filters, including `product_ids`, `order_status`,
`order_side`, `order_ids`, `start_date`/`end_date`, `order_types`,
`product_type`, `time_in_forces`, and `sort_by`:

```{r get-orders}
orders <- trading$get_orders(
  product_ids = "BTC-USD",
  order_status = "OPEN",
  limit = 10,
  sort_by = "LAST_FILL_TIME"
)
orders[, .(order_id, product_id, side, status, order_type, filled_size)]
```

### Query Fills

`get_fills()` retrieves historical fills. Filter by `order_ids` (plural),
`trade_ids`, `product_ids`, the `start_sequence_timestamp` /
`end_sequence_timestamp` bounds, and `sort_by`:

```{r get-fills}
fills <- trading$get_fills(
  product_ids = "BTC-USD",
  sort_by = "TRADE_TIME"
)
fills[, .(trade_id, order_id, side, price, size, commission)]
```

### Cancel Orders

`cancel_orders()` cancels one or more open orders by id and returns per-order
results:

```{r cancel-orders}
cancelled <- trading$cancel_orders(order_ids = c(order$order_id))
cancelled[, .(order_id, success, failure_reason)]
```

---

## Asynchronous Use

Every class works in async mode too. Pass `async = TRUE` and each method returns
a [promise][promises::promise] instead of a `data.table`. The recommended idiom
is `coro::async()` / `await()` for sequential-looking code, driving the event
loop with [later](https://r-lib.github.io/later/):

```{r async}
market_async <- CoinbaseMarketData$new(async = TRUE)

main <- coro$async(function() {
  ticker <- await(market_async$get_ticker(product_id = "BTC-USD"))
  candles <- await(market_async$get_ohlcv(product_id = "BTC-USD", granularity = "1min"))

  print(ticker)
  print(candles)
  return(invisible(NULL))
})

main()

# Drain the event loop until every promise has resolved.
while (!later$loop_empty()) {
  later$run_now()
}
```

---

## Next Steps

- See `vignette("async-usage")` for promise-based asynchronous operation.
- See `vignette("futures-shorting")` for US futures (CFM) balances, positions,
  and the short leg via `CoinbaseFutures`.
- Browse the [pkgdown site](https://dereckscompany.github.io/coinbase/) for full
  method documentation.
- For bulk historical data collection, see `?coinbase_backfill_trades`.
